Applying Radial Basis Function Networks and Markov Chains for on-line detection of concept drift in non-stationary environments

### 2019-10-28 tex/article/article.tex
up

\begin{itemize}
    \item \textbf{Explicit Algorithms/Supervised}: These methods adopt a passive approach, as they depend on the correct labeling of the data.
    The model performance is monitored continuously, and drifts are detected when its performance starts to deteriorate, passing past a threshold.
    \item \textbf{Implicit Algorithms/Unsupervised:} These algorithms take a proactive approach and are independent of correct data labeling.
    Concept drifts are detected through the analysis of incoming data or of indicators produced by the applied learning techniques.
    Although they are more prone to false alarms, they are an alternative to scenarios where obtaining labels is expensive, time-consuming or unviable.
    Also, this approach can lead to better results, since it is possible to refit the model or adjust the data before the deterioration of the predictions.
\end{itemize}

>>>>

\begin{itemize}
    \item \textbf{Explicit Algorithms/Supervised}: Adopt a passive approach, as they depend on the correct labeling of the data.
    The model performance is monitored continuously, and drifts are detected when its performance starts to deteriorate, passing past a threshold.
    \item \textbf{Implicit Algorithms/Unsupervised:} Implement a proactive approach and are independent of correct data labeling.
    Concept drifts are detected through the analysis of incoming data or indicators produced by the applied learning techniques.
    Although they are more prone to false alarms, they are an alternative to scenarios where obtaining labels is expensive, time-consuming or unviable.
    Also, this approach can lead to better results, since it is possible to refit the model or adjust the data before the deterioration of the predictions.
\end{itemize}
